---
title: "Visits_to_Syc"
author: "Emmanuel Lourie"
date: "28 4 2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list=ls()) # clean history 
library(tidyverse)

#stops_small<-read_csv("data/Data_for_Information_analysis_small_cluster2021-11-07.csv") # after arrange #1 & 2 (prep data for information)
#syc_stops_small<-stops_small[stops_small$tree_sp=="Ficus sycomorus",]
#syc_stops_small<-syc_stops_small[!is.na(syc_stops_small$TAG),]

#write.csv(syc_stops_small,"stops_on_syc_small1.csv")

```

```{r}
all_stops<-read_csv("data/stops_for_caves_w_short_ForSyc2022-05-02.csv")
stops_syc<-read_csv("data/Neot_visits_buff100.csv") # All short stops within 100 m buffer around Neot syc (done in ArcGIS)
aggregate(stops_syc$TAG, list(stops_syc$cave_origin), function(x)length(unique(x)))
aggregate(stops_syc$TAG_Night, list(stops_syc$cave_origin), function(x)length(unique(x)))

table(all_stops$dummy)
all_stops<-all_stops[all_stops$dummy=="no",]
# Take only Northern caves
#all_stops<-all_stops[all_stops$cave_origin %in% c("Einan", "Zemer cave","Shaked"),]

# When were the syc visits?
hist(lubridate::hour(stops_syc$time_start),breaks=100)

sure_syc<-stops_syc[stops_syc$tree_sp=="Ficus sycomorus",]
hist(lubridate::hour(sure_syc$time_start),breaks=100)
hist(sure_syc$duration)
sure_syc<-sure_syc[sure_syc$duration>1,]
hist(lubridate::hour(sure_syc$time_start),breaks=100)
stops_syc_long<-stops_syc[stops_syc$duration>4,]
table(lubridate::hour(stops_syc_long$time_start))
table(lubridate::hour(stops_syc_long$time_end))

# looks like from 19 to 22 UTC
# For the summer this is 22:00- 01:00
# based on end-times, normally ends between 19 to 22 UTC
# So most chances to see them is 22:oo-00:00
```

```{r}
table(stops_syc$dummy)
#stops_syc<-stops_syc[stops_syc$cave_origin %in% c("Einan", "Zemer cave","Shaked"),]
syc_tag_nights<-unique(stops_syc$TAG_Night)
stops_no_syc<-all_stops[!all_stops$TAG_Night %in% syc_tag_nights,]
stops_no_syc<-stops_no_syc[!duplicated(stops_no_syc$TAG_Night),]
stops_no_syc$syc<-rep("no",nrow(stops_no_syc))
stops_syc_unq<-stops_syc[!duplicated(stops_syc$TAG_Night),]
stops_syc_unq$syc<-rep("yes",nrow(stops_syc_unq))
cols<-colnames(stops_syc_unq)
stops_no_syc<-stops_no_syc[,cols]

syc_dt<-rbind(stops_syc_unq, stops_no_syc)
table(syc_dt$syc)

# Here load the data of dates without fruits
phen_table <- read.table(text = "  Start        End  stage
1	2019-11-11	2020-01-14	no_fruits
2	2020-01-15	2020-06-01	NA
3	2020-06-02	2020-06-22	no_fruits
4	2020-06-23	2020-06-25	manipulation
5	2020-06-26	2020-07-31	no_fruits
6	2020-08-01	2020-08-30	fruits
7	2020-09-01	2020-10-17	no_fruits
8	2020-10-18	2020-11-01	fruits
9	2020-11-02	2021-11-30	NA
10	2020-12-01	2021-03-30	no_fruits
11	2019-12-15	2020-02-15	no_fruits
12	2018-12-15	2019-02-15	no_fruits", # Add winters artificially
header = TRUE,
stringsAsFactors = FALSE)

# With any fruit (ripe or not)
phen_table <- read.table(text = "  Start        End  stage
1	2019-11-11	2020-01-14	no_fruits
2	2020-01-15	2020-06-01	NA
3	2020-06-02	2020-06-12	fruits
4	2020-06-13	2020-06-22	no_fruits
5	2020-06-23	2020-06-25	manipulation
6	2020-06-26	2020-06-30	no_fruits
7	2020-07-01	2020-11-01	fruits
8	2020-11-02	2020-11-30	NA
9	2020-12-01	2021-03-30	no_fruits
11	2019-12-15	2020-02-15	no_fruits
12	2018-12-15	2019-02-15	no_fruits", # Add winters artificially
header = TRUE,
stringsAsFactors = FALSE)




phen_table$Start<-as.Date(phen_table$Start, format="%Y-%m-%d")
phen_table$End<-as.Date(phen_table$End, format="%Y-%m-%d")

phen_start<-min(phen_table$Start)
phen_end<-max(phen_table$End)


```

Week global
```{r}
# Global weeks:

syc_dt<-syc_dt[!is.na(syc_dt$date_global),]
class(syc_dt$date_global)
start_date<-min(syc_dt$date_global); end_date<-max(syc_dt$date_global)
weeks_dates<-seq(start_date,end_date+6, 7)
weeks_inx<-seq(1, length(weeks_dates),1)
weeks_df<-data.frame("start_date"=weeks_dates, "week_inx"=weeks_inx)
date_l<-unique(weeks_df$start_date)
syc_dt$week_global<-rep(NA,nrow(syc_dt))


#d<-200
for (d in 1:length(date_l)){
week_loc<-which(syc_dt$date_global>= date_l[d] & syc_dt$date_global< date_l[d+1])
if(length(week_loc)>0){
syc_dt$week_global[week_loc]<-weeks_df$week_inx[weeks_df$start_date==date_l[d]]
 }
}

syc_dt$TAG_week_global<-paste0(syc_dt$TAG,"_", syc_dt$week_global)
syc_dt<-syc_dt %>% group_by(week_global) %>% mutate("week_date"=min(as.Date(date_global))) 
syc_dt_all<-syc_dt

syc_dt<-syc_dt[syc_dt$date_global>=phen_start & syc_dt$date_global<=phen_end,]

```

3-day intervals (fitting to the time the manipulation created an effect)
```{r}
man_start<-na.omit(phen_table$Start[phen_table$stage=="manipulation"])
man_end<-na.omit(phen_table$End[phen_table$stage=="manipulation"])
before_man<-seq(man_start-1,start_date, -3)
after_man<-seq(man_end+1, end_date,3)
man<-seq(man_start,man_end,3)
triple_dates<-c(before_man,man,after_man)
triple_inx<-seq(1, length(triple_dates),1)
triple_df<-data.frame("start_date"=triple_dates, "triple_inx"=triple_inx)

# add penology
syc_dt_all$fruits<-NA
for (r in 1:nrow(phen_table)){
rows<-which(syc_dt_all$date_global>=phen_table$Start[r] & syc_dt_all$date_global<=phen_table$End[r])
syc_dt_all$fruits[rows]<-phen_table$stage[r]
}
table(syc_dt_all$fruits, useNA = "ifany")

triple_df<-triple_df[order(triple_df$start_date),]
tdate_l<-unique(triple_df$start_date)
syc_dt_all$triple_date<-rep(NA,nrow(syc_dt_all))

for (t in 1:length(tdate_l)){
triple_loc<-which(syc_dt_all$date_global>= tdate_l[t] & syc_dt_all$date_global< tdate_l[t+1])
if(length(triple_loc)>0){
syc_dt_all$triple_date[triple_loc]<-triple_df$triple_inx[triple_df$start_date==tdate_l[t]]
 }
}

syc_dt_all$TAG_triple<-paste0(syc_dt_all$TAG,"_", syc_dt_all$triple_date)
syc_dt_all<-syc_dt_all %>% group_by(triple_date) %>% mutate("tdate"=min(as.Date(date_global)))

```

```{r}
syc_dt_sum<-syc_dt %>% group_by(TAG, week_date, TAG_week_global) %>% summarise("n_syc"=length(syc[syc=="yes"]),"no_syc"=length(syc[syc=="no"]),"all_nights"=length(syc))
syc_dt_sum2<-syc_dt_sum[syc_dt_sum$all_nights>=4,]
syc_dt_sum2$prop_vis<-round(syc_dt_sum2$n_syc/syc_dt_sum2$all_nights,digits = 2)

syc_dt_sum3<-syc_dt_sum2 %>% group_by(week_date) %>% summarise("prop_vis"=mean(prop_vis, na.rm=T), "n_bats"=length(unique(TAG)))

# add penology
syc_dt_sum3$fruits<-NA
for (r in 1:nrow(phen_table)){
rows<-which(syc_dt_sum3$week_date>=phen_table$Start[r] & syc_dt_sum3$week_date<=phen_table$End[r])
syc_dt_sum3$fruits[rows]<-phen_table$stage[r]
}
table(syc_dt_sum3$fruits)
```

plot
```{r}
ggplot(data=syc_dt_sum3, aes(x=week_date, y=prop_vis+0.01, fill=fruits))+geom_col()+theme_classic()
```

Not enough data for weeks (60 weeks during 2019-2021).
Also, not enough tags for when there were fruits in Neot ()
Try per night
```{r}
syc_sum_night<-syc_dt_all %>% group_by(date_global)%>% summarise("syc_vis"=length(syc[syc=="yes"]),"n_bats"=length(unique(TAG)))
syc_sum_night$prop_syc<-round(syc_sum_night$syc_vis/syc_sum_night$n_bats, digits=2)
syc_sum_night$fruits<-NA
# add penology
syc_dt_sum3$fruits<-NA
for (r in 1:nrow(phen_table)){
rows<-which(syc_sum_night$date_global>=phen_table$Start[r] & syc_sum_night$date_global<=phen_table$End[r])
syc_sum_night$fruits[rows]<-phen_table$stage[r]
}

table(syc_sum_night$fruits, useNA = "ifany")

```

plot
```{r}
syc_sum_night2<-syc_sum_night[syc_sum_night$n_bats>=4,]
ggplot(data=syc_sum_night2, aes(x=date_global, y=prop_syc+0.01, fill=fruits))+geom_col()+theme_classic()


```

# During the manipulation, some bats racted immediatly, and some upt to 3 nights after. So it makes sense to ask if there was a visit during 3 nights (and compare to normal periods)
```{r}
syc_dt_sum_t<-syc_dt_all %>% group_by(fruits,TAG, tdate) %>% summarise("n_syc"=length(syc[syc=="yes"]))
syc_dt_sum_t$syc_vis<-ifelse(syc_dt_sum_t$n_syc>0,1,0)

syc_sum_triple<-syc_dt_sum_t %>% group_by(fruits,tdate) %>% summarise("n_syc_vis"=sum(syc_vis), "n_tags"=length(unique(TAG)))
syc_sum_triple$syc_prop<-syc_sum_triple$n_syc_vis/syc_sum_triple$n_tags
```

# Check on Kamadata what happens when there are visits with no fruits:
```{r}
no_fruits_vis<-syc_sum_night[syc_sum_night$fruits=="no_fruits" & syc_sum_night$syc_vis>0,]
no_fruits_vis<-no_fruits_vis[!is.na(no_fruits_vis$date_global),]
ex<-syc_dt[syc_dt$date_global=="2019-12-22",]
```

Box plots - I don't have enough (1) phenology when the bats are tracked, and in particular (2) tags tracked when there are fruits in Neot. So I will compare the total probability (no matter the season) to the probability when there are no fruits (subset) to the probability during the manipulation.

```{r}
syc_sum_triple1<-syc_sum_triple
syc_sum_triple1$fruits<-"All"
syc_sum_triple_nof<-syc_sum_triple[syc_sum_triple$fruits=="no_fruits",]
syc_sum_triple_man<-syc_sum_triple[syc_sum_triple$fruits=="manipulation",]
syc_sum_tnight_all<-rbind(syc_sum_triple1, syc_sum_triple_nof, syc_sum_triple_man)
syc_sum_tnight_all<-syc_sum_tnight_all[!is.na(syc_sum_tnight_all$fruits),]
syc_sum_tnight_all$syc_prop<-round(syc_sum_tnight_all$syc_prop,digits=2)

syc_sum_tnight_all2<-syc_sum_tnight_all[syc_sum_tnight_all$n_tags>2,]


syc_sum_tnight_all3<-syc_sum_tnight_all2[syc_sum_tnight_all2$fruits!="manipulation",]
man_val<-na.omit(syc_sum_triple_man$syc_prop)

ggplot(data=syc_sum_tnight_all3, aes(x=syc_prop, fill=fruits))+geom_histogram(position="dodge")+theme_bw()+
  geom_vline(xintercept = man_val,linetype="longdash")+xlab("Probability to visit Sycamore fig in three nights") + ylab("Frequency")+   
    scale_fill_discrete(name = "Phenological stage", labels = c("All", "No fruits")) + theme(text = element_text(size = 20)) 

freq_table<-table(syc_sum_tnight_all3$fruits, syc_sum_tnight_all3$syc_prop)
prop_table<-as.data.frame(prop.table(freq_table))
colnames(prop_table)<-c("fruits","syc_prop" ,"proportion")
prop_table$proportion<-round(prop_table$proportion,digits=2)

prop_table_all<-prop_table[prop_table$fruits=="All",]
prop_table_all$syc_prop<-as.double(as.character(prop_table_all$syc_prop))

ggplot(data=prop_table_all, aes(y=proportion,x=syc_prop))+geom_col(position="dodge")+theme_bw()+xlab("Probability to visit Sycamore fig in three nights") + ylab("Proportion") + theme(text = element_text(size = 20))+
  geom_vline(xintercept = 0.25,linetype="longdash")+ 
 scale_x_continuous(breaks=seq(0,0.75,0.15)) 

ggplot(data=prop_table, aes(x=syc_prop,y=proportion, fill=fruits))+geom_col(position="dodge")+theme_bw()+
  geom_vline(xintercept = 0.37,linetype="longdash")+xlab("Probability to visit Sycamore fig in three nights") + ylab("Proportion")+   
    scale_fill_discrete(name = "Phenological stage", labels = c("All", "No fruits")) + theme(text = element_text(size = 20))

ggplot(data=syc_sum_tnight_all3, aes(x=fruits, y=syc_prop))+geom_boxplot(outlier.shape = NA)+geom_point(color="purple", position="jitter")+theme_bw()+
  geom_hline(yintercept = man_val,linetype="longdash")+ylab("Probability to visit Sycamore fig in three nights") + xlab("")+ scale_x_discrete(labels=c("All" = "All periods", "no_fruits" = "No fruits"))+ theme(text = element_text(size = 20)) 

ex<-syc_dt_sum_t[syc_dt_sum_t$tdate=="2019-12-22",]

```

Chi square test
```{r}
table(syc_sum_tnight_all$fruits)
syc_sum_test<-syc_sum_tnight_all %>% group_by(fruits) %>% summarise("n_vis" = sum(n_syc_vis),"n_tags"=sum(n_tags))
# Fix based on my previouse counts:
syc_sum_test$n_vis[syc_sum_test$fruits=="manipulation"]<-14#13
syc_sum_test$n_tags[syc_sum_test$fruits=="manipulation"]<-71#49
#syc_sum_test<-syc_sum_test[syc_sum_test$fruits!="All",]
no_fruits_prop<-syc_sum_test$n_vis[syc_sum_test$fruits=="no_fruits"]/syc_sum_test$n_tags[syc_sum_test$fruits=="no_fruits"]

manipulation_prop<-syc_sum_test$n_vis[syc_sum_test$fruits=="manipulation"]/syc_sum_test$n_tags[syc_sum_test$fruits=="manipulation"]

all_prop<-syc_sum_test$n_vis[syc_sum_test$fruits=="All"]/syc_sum_test$n_tags[syc_sum_test$fruits=="All"]

manipulation_prop/all_prop

syc_sum_test$did_not<-syc_sum_test$n_tags-syc_sum_test$n_vis
syc_sum_test_chi<-syc_sum_test[,-3]
syc_sum_test_chi<-as.matrix(syc_sum_test_chi[,-1])
print(chisq.test(syc_sum_test_chi)) # among all groups

# against non-fruits only
syc_nof_test_chi<-as.matrix(syc_sum_test_chi[-1,])
print(chisq.test(syc_nof_test_chi))
print(fisher.test(syc_nof_test_chi, alternative = "greater")) # checking if there are greater probabilities for manipulation vs. no fruits (odds ratio > 1) 

# against all fruits 
syc_all_test_chi<-as.matrix(syc_sum_test_chi[-3,])
print(chisq.test(syc_all_test_chi))


```
 
